\documentclass{article}
 
\begin{document}

\section{Flight Instructions}
\subsection{Pre-Flight}
Checks:
\begin{itemize}
\item Check that all subsystems are plugged in
\item Check that propeller holders are screwed on solidly and are tight
\item Check that all screws are tight
\item Check battery charge level
\item Check that all wires are tied or taped down well and will not interfere with propeller movement
\item Check that controller voltage is near maximum
\end{itemize}
\subsection{First Flight}
Your first flight should be performed with the quadcopter tied down solidly and so that it can not flip. The quadcopter is armed by pushing both control sticks down and to the right for 4 seconds. Do so. The blades should begin to spin gently.\\
\indent The optimal control scheme is as follows:
\begin{itemize}
\item Left stick vertical motion should increase or decrease vertical thrust.\\
\item Left stick horizontal motion should induce in-place rotation of the quadcopter.\\
\item Right stick vertical motion should cause the quadcopter to move forwards if the stick is moved in the up direction, and backwards if moved in the down direction.\\
\item Right stick horizontal motion should cause the quadcopter to move left if the stick is moved in the left direction, and right if moved in the right direction.\\
\end{itemize}
Note that the directions given are with respect to the quadcopter's current orientation.\\
\indent While the blades are spinning slowly, slowly increase thrust until the quadcopter is near takeoff, but not until it actually lifts off. Then move all controls slightly to check whether they are bound properly. The sticks may be switched, directions may be inverted, and/or controls may be swapped. If they are, land, and after disarming the quadcopter (by pushing both control sticks down and to the left, and holding it for 4 seconds), switch them until they are right.\\
\indent Once the controls are corrected, re-arm the copter and take off.\\
\indent Once in the air, practice keeping the copter stable in the air. After becoming successful at this, begin moving it slowly in various directions and getting the feel for it. Everything else is just becoming more familiar with the controls.\\
Some important things to remember:
\begin{itemize}
	\item The quadcopter has finite battery. If you are not using MavLink to monitor it, land as soon as responsiveness begins to drop noticeably.
	\item If the quadcopter goes out of range, it will keep flying in its current direction (unless MavLink tells it otherwise). Keep it close
	\item Wireless interference may affect range.
	\item Props can be replaced; humans can't. Dont fly close to people.
\end{itemize}

\end{document}
